---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "README-"
)
```

# cookr

The goal of cookr is to track in real time the results of the 2018 US congressional election by district using a live [google spreatsheet](https://docs.google.com/spreadsheets/d/1WxDaxD5az6kdOjJncmGph37z0BPNhV1fNAH_g7IkpC0/htmlview?sle=true#gid=326900537) populated by [Cook political report](https://www.cookpolitical.com/), and add historical context of reported results using [Ballotpedia](https://ballotpedia.org/).

The package locates which districts are still active and searches for adjacent districts to get their restults too, using this [geojson file](https://gist.githubusercontent.com/mbostock/4090846/raw/d534aba169207548a8a3d670c9c2cc719ff05c47/us-congress-113.json).

In the package there is a plotting function to vizualize the time depedent results.

Sticking a pin in this is to have data to model in the future expected voter turnout with higher frequency data.

## Installation

You can install cookr from github with:

```{r gh-installation, eval = FALSE}
# install.packages("remotes")
remotes::install_github("yonicd/cookr")
```

## Usage

### Load Library

```{r}
library(cookr)
```

### Fetching The Spreadsheet

```{r}
cook_data <- cookr::fetch_spreadsheet()
```

Peek at Data

```{r}
cook_data%>%
  dplyr::glimpse()
```

Filter to open districts

```{r}
open_districts <- cook_data%>%
  cookr::cook_open()
```

Find the adjacent districts

```{r}
adjacent_districts <- open_districts%>%
  cookr::cook_adjacent()
```

Combine Data

```{r}
districts <- dplyr::bind_rows(open_districts,adjacent_districts)
```

```{r}
districts%>%
  dplyr::glimpse()
```

Fetch Historical Results of the Districts From Ballotpedia

```{r}
cook_history <- districts%>%
  cook_ballotpedia()
```

```{r}
cook_history%>%
  dplyr::glimpse()
```

### Plotting

```{r,fig.height=7,fig.width=7}
p <- cook_history%>%
  cook_plot()

p
```
 
### Saving 
 
```{r,eval=FALSE}
ggsave(p,filename = sprintf('plots/cook_%s.png',strftime(Sys.Date(),format = '%Y_%m_%d')))

saveRDS(cook_html,file = sprintf('src_data/cook_spreadsheet_%s.rds',strftime(Sys.Date(),format = '%Y_%m_%d')))

```